%-------------------------
% Resume in LaTeX
% Author: Jake Gutierrez
% Based on: https://github.com/sb2nov/resume
% License: MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generate PDF is machine-readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]} 
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Oluwafunmito Adedeji} \\ \vspace{1pt}
    \small No 4, Road 3, Line 1, Modomo, Ajebandele, Ile-Ife, Osun State, Nigeria $|$ 
    \href{tel:+2349013669407}{\underline{+234 901 366 9407}} $|$ 
    \href{mailto:adedejioluwafunmito2004@gmail.com}{\underline{adedejioluwafunmito2004@gmail.com}} $|$
    \href{https://linkedin.com/in/oluwafunmito-adedeji-675b96305}{\underline{linkedin.com/in/oluwafunmito-adedeji}} $|$
    \href{https://github.com/Oluwafunmito2004}{\underline{github.com/Oluwafunmito2004}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Obafemi Awolowo University}{Ile Ife, Osun State}
      {Bachelor of Science in Electronics and Electrical Engineering}{Jan. 2022 -- Present}
      \resumeItemListStart
        \resumeItem{Relevant Coursework: Electric Circuit Theory, Electronics and Electrical Materials, Computer Programming, Introduction to Computer Packages, Microelectronic Devices and Circuits, Computational Structures, Measurement and Instrumentation, Engineering Analysis, Electrical Machine}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {SWEP Program}{Ile Ife, Osun State}
      {Electronics and Electrical Engineering School Internship}{Aug. 2024 -- Sep. 2024}
      \resumeItemListStart
        \resumeItem{Designed and simulated custom PCB layouts for IoT and automation applications using Proteus}
        \resumeItem{Created logic and control algorithms for microcontrollers (Arduino, ESP32) ensuring seamless hardware-software integration }
      \resumeItemListEnd
      
    \resumeSubheading
      {Logic Module Development for Automated Systems}{Ile Ife, Osun State}
      {Embedded Systems Developer}{Aug. 2024 -- Present}
      \resumeItemListStart
        \resumeItem{Designed control logic for solar-powered automated lawn mower, optimizing motor control algorithms}
        \resumeItem{Implemented geofencing techniques for precise navigation and mowing coverage}
        \resumeItem{Designed logic for automated housing system, optimizing fan and shutter control for temperature control}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Solar Powered Automated Lawnmower} $|$ \emph{Proteus, Arduino}}{Aug. 2024}
          \resumeItemListStart
            \resumeItem{Designed and implemented control systems for autonomous operation using microcontroller programming}
            \resumeItem{Integrated solar charging system with power management for continuous operation}
            \resumeItem{Developed navigation algorithms for efficient area coverage and obstacle avoidance}
          \resumeItemListEnd

      \resumeProjectHeading
          {\textbf{Automated Housing Ventilation System} $|$ \emph{Arduino}}{Dec. 2024 -- Mar. 2025}
          \resumeItemListStart
            \resumeItem{Led a team in designing and developing an automated temperature control system for residential spaces}
            \resumeItem{Implemented sensor integration with Arduino Nano for real-time temperature-based fan and shutter control}
            \resumeItem{Collaborated on PCB layout design for reliable signal transmission between components}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, C++, HTML/CSS} \\
     \textbf{Developer Tools}{: VS Code, Arduino, MatLab, Labview, LTSpice} \\
     \textbf{Technologies/Frameworks}{: Linux, GitHub, Proteus} \\
     \textbf{Hardware}{: Microcontrollers (Arduino, ESP32), PCB Design}
    }}
 \end{itemize}

%-----------LEADERSHIP-----------
\section{Leadership \& Extracurricular}
  \resumeSubHeadingListStart
    \resumeSubheading
      {NACOS OAU [Innofest 1.0]}{Ile Ife, Osun State}
      {Head of Partnership}{Oct. 2024 -- Feb. 2025}
      \resumeItemListStart
        \resumeItem{Spearheaded strategic collaborations and secured key partnerships for technology innovation festival}
        \resumeItem{Negotiated sponsorships to support event objectives}
      \resumeItemListEnd

    \resumeSubheading
      {Union of Genius (UOG)}{Ile Ife, Osun State}
      {Head of Web Development Team}{Jun. 2021 -- Present}
      \resumeItemListStart
        \resumeItem{Led team in developing and maintaining the organization's web presence}
        \resumeItem{Coordinated with other departments to implement technical solutions for organizational needs}
        \resumeItem{Visited secondary school to teach students the basics of web development (HTML/CSS)}
      \resumeItemListEnd

    \resumeSubheading
      {Automated Housing Ventilation System Project}{Obafemi Awolowo University}
      {Team Lead}{Dec. 2024 -- Mar. 2025}
      \resumeItemListStart
        \resumeItem{Led the team to conceptualize, organize, and execute the development of a home ventilation automation solution}
        \resumeItem{Coordinated team efforts, project planning, and final presentation during academic showcase}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
